Stable Neo-Hookean Flesh Simulation

### 2019-12-02 LaTeX-Master-Vorlage/chapter/Background.tex
i dont even know

\subsection{Polar Decomposition of the Deformation Gradient}
With the help of mathematics we can decompose the deformation gradient in the following form:

@@

@@

In the context of flesh simulations we use the poisson's ratio as a characterization for the resistance to volume change of flesh. Biological tissues such as flesh, fat and muscles have one important property: Volume preservation. As a result the poisson's ratio is a higher value, meaning it is found in the range between 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.

The calculation of the poisson's ratio defined as in equation \ref{eq:poisson} is a challenge. Fortunately we can make use of the \textit{Lamé Parameters}. These are the two constants $\mu$ and $\lambda$ that are specific for a material. With the help of these two constants we can transform equation \ref{eq:poisson} into the following form:

@@

This equation allows us to calculate the poisson's ratio much easier.

@@

\subsection{Deformation Energy}
In order to get a convincing simulation of high quality we must choose an appropriate energy. In the case of modelling deformations on human-like characters we have to choose an elastic energy. The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back into its rest shape.
\\
The energy then has to be minimized in order to get the results we want.

\begin{definition}
  This is a definition.
\end{definition}

>>>>

\subsubsection{Polar Decomposition of the Deformation Gradient}
With the help of mathematics one can decompose the deformation gradient in the following form:

@@

\todoredefined[inline]{
TODO: Explain more here.
}

@@

In the context of flesh simulations I use the poisson's ratio as a characterization for the resistance to volume change of flesh. Biological tissues such as flesh, fat and muscles have one important property: Volume preservation. As a result the poisson's ratio is a higher value, meaning it is found in the range between 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.

The calculation of the poisson's ratio defined in equation \ref{eq:poisson} is a challenge. Fortunately we can make use of the \textit{Lamé Parameters}. These are the two constants $\mu$ and $\lambda$ that are specific for a material. With the help of these two constants one can transform the equation \ref{eq:poisson} into the following form:

@@

This equation allows to calculate the poisson's ratio much easier.

@@

\subsection{Deformation Energy}
In order to get a convincing simulation of high quality one must choose an appropriate energy. In the case of modelling deformations on human-like characters an elastic energy needs to be chosen. The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back into its rest shape.
\\
The energy then has to be minimized in order to get the results we want.

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
i dont even know

\chapter{Paper} \label{c:Paper}
In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}. In the interest of understanding the thought process of the authors I will include some of their calculations a bit more detailed. In addition examples and visualisations should help for a better perception.

>>>>

\chapter{Paper} \label{c:Paper}
In this chapter I will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}. In the interest of understanding the thought process of the authors I will include some of their calculations a bit more detailed. In addition examples and visualisations should help for a better perception.
